\Title

### 2021-01-07 manuscript/manuscript.tex
Rephrase lambda values part as a suggestion

\noindent where $\lambda$ is a \emph{dimensionless} damping parameter and
regularization is applied on the scaled coefficients $\mathbf{m}$ instead of
$\mathbf{c}$.
In practice, we find that suitable $\lambda$ values fall between $10^{-8}$ and
$10^{-1}$, irrespective of the dataset, and that results are mostly sensitive
to order-of-magnitude changes in $\lambda$.

>>>>

\noindent where $\lambda$ is a \emph{dimensionless} damping parameter and
regularization is applied on the scaled coefficients $\mathbf{m}$ instead of
$\mathbf{c}$.
From experience, we recommend searching for suitable $\lambda$ values between
$10^{-8}$ and $10^{2}$ varying by order-of-magnitude, irrespective of the
dataset.
